The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-18 writing/draft3/draft15.tex
estimating testing working hard

We further applied a series of likelihood ratio tests of significance of random slopes, however no subset of random slopes improved the fit, hence, our final model only includes random intercepts.\footnote{Although including the coefficient of variation of temperature as a random effect instead of the random intercepts does improve the AIC from $2164.7$ to $2163.1$ (these AIC values differ from those presented in table~\ref{ARMA} in the appendix as the current models do not account for the error autocorrelation structure due to convergence issues of the model with the random slope) we decided not to include the coefficient of variation of temperature in the random effects. The reason for not including the random slope is that the difference in AIC is negligible and F-test of the comparison of the two models is marginally insignificant favouring the simpler model (p-value$=0.059$).}

>>>>

We further applied a series of likelihood ratio tests of significance of random slopes, however no subset of random slopes improved the fit, hence, our final model only includes random intercepts.\footnote{Although adding the random slope of the coefficient of variation slightly improved the AIC from $2122.226$ to $2122.110$, we decided to not to include the coefficient of variation of temperature in the random effects. The reason for not including the random slope is that the difference in AIC is negligible and the F-test of the comparison of the two models is insignificant favouring the simpler model (p-value$=0.128$).}
